\textbf{ Discovery of a disrupting open cluster far into the Milky Way halo:\\ a recent star formation event in the leading arm of the Magellanic stream?}

### 2018-11-10 ms.tex
ack

It is a pleasure to thank
Lauren Anderson (Flatiron),
Ana Bonaca (Harvard),
Elena D'Onghia (UW Madison),
Dan Foreman-Mackey (Flatiron),
Raja Guhathakurta (UCSC),
Cliff Johnson (Northwestern),
Ekta Patel (Arizona),
Josh Peek (STScI),
Anil Seth (Utah),
and Erik Tollerud (STScI)
for useful suggestions and discussion.

>>>>

It is a pleasure to thank
Lauren Anderson (Flatiron),
Ana Bonaca (Harvard),
Elena D'Onghia (UW Madison),
Dan Foreman-Mackey (Flatiron),
Raja Guhathakurta (UCSC),
Cliff Johnson (Northwestern),
Ekta Patel (Arizona),
Sarah Pearson (Flatiron),
Josh Peek (STScI),
Anil Seth (Utah),
and Erik Tollerud (STScI)
for useful suggestions and discussion.
